

This paper proposes a new mixed integer linear mathematical programming (MILP) model, dubbed 3D-SCPTOP, for procurement transport planning in manufacturing supply chains. The model effectively integrates procurement and transport decisions while accounting for three-dimensional full-truck loading constraints and managing returnable transport items (RTIs). Thus, we optimise the material to procure for an assembly manufacturing site, RTIs closed-loop management,  and the involved transport decisions, including the truck loading configuration. Procurement transport decisions are based on the demand of assemblers, the supplier's inventory levels, and the dimensions of the truck / RTIs. The optimisation model aims to minimise transportation and inventory costs. As the 3D loading problem is NP-hard, a matheuristic (Math-3D-SCPTOP) approach is developed to obtain good quality solutions for large instances in an efficient computational time. The 3D-SCPTOP model was validated with a case study in an automotive seating first-tier supplier. Regarding inventory and transport efficiency, the results of the 3D-SCPTOP model are superior to the company procedures.

\keywords{ Procurement, inventory, transport planning,  full-truckload, 3D container loading }
\section{Introduction}

\section{Literature Review}
\subsection{Procurement transport and inventory planning}
\section{Graph based matehmatical model}
Now we will define a new form of understanding mathematial model. With this new paradigm, we will be able to define a new paradigm to model.

We will first define it for mathematical programming models where we just have the matrix. 

That is, we are going to define it for Linear programs, later we will abstract it and use for MILP models, where the variables and parameters are indexed.

A Linear Program is just a 

\begin{align}
  \min c \cdot x \\
  Ax = b
\end{align}

We therefore have $x_i$ variables, $a_{ij}$ parameters and $b_j$ parameters and $c_i$ pareameters for the objective function.

$c_i \sim{ x_i}$ if $c_i\neq 0$.

$b_j \sim { j }$ if $c_i\neq 0$.
