This paper proposes a new mixed integer linear mathematical programming (MILP) model, dubbed as SND-RTI (Service Network Design for Returnable Transport Items), for procurement transport planning in manufacturing supply chains. 
The model integrates transport decisions while accounting for managing returnable transport items (RTIs).
Thus, we optimise the strategic decisions in terms of allocated RTIs, purchased RTIs, direct and return routes and Q-days.
The optimisation model aims to minimise transportation and inventory costs.
Regarding inventory and transport efficiency, the results of the 3D-SCPTOP model are superior to the company procedures.

\keywords{ Procurement, inventory, transport planning,  full-truckload, 3D container loading }
\section{Introduction}

\section{Literature Review}

\subsection{Research Gaps \& Methodology}

\input{figures/tikz/tikz_definitions.tex}
\input{problemStatement.tex}

Given:
\begin{itemize}
    \item Flow of full RTIs across the supply chain.
    \item Safety Stocks of the supply chain nodes.
    \item Economic and environmental Transport Costs across the supply chain.
\end{itemize}


To determine:

 \begin{itemize}
     \item Transport decisions, including routes and method of transport.
     \item Number of RTIs needed in the network.
 \end{itemize}

 

KPIs: One to One comparison. 
% \input{models/base.tex}

% \input{models/base_q.tex}:while
\input{models/base_new.tex}

% \input{models/formal-logic-definition.tex}

% \input{models/compact.tex}

