\section{Mathematical Model}



% ══════════════════════════════════════════════════════════════════
%  NOMENCLATURE
% ══════════════════════════════════════════════════════════════════

\begin{longtable}{|p{0.17\textwidth}|p{0.79\textwidth}|}
\caption{Model nomenclature}
\label{tab:nomenclature}\\
\hline
\multicolumn{2}{|l|}{\textbf{Indices and Sets}}\\ \hline
$V$
  & Set of nodes representing manufacturing plants; $i, j \in V$ \\
$E$
  & Set of directed edges representing potential transport routes;
    $E = V \times V$ \\
\hline
\multicolumn{2}{|l|}{\textbf{Parameters}}\\ \hline
$\mu_{ij}$
  & Daily average demand on route $(i,j)$, expressed in RTI units \\
$ric_{ij}$
  & Fraction of full shipments on route $(i,j)$ that require
    a return inlay \\
$c_{ij}$
  & Transport cost per unit volume on route $(i,j)$ \\
$f_{ij}$
  & Fixed dispatch cost per shipment on route $(i,j)$ \\
$v^{f},\ v^{e}$
  & Volume occupied by one full and one empty RTI, respectively \\
$l_{ij}$
  & Transit time on route $(i,j)$, in days \\
$q^{\min},\ q^{\max}$
  & Minimum and maximum queue time, in days \\
$\alpha^{f},\ \alpha^{e}$
  & Maintenance loss factor applied to full and empty RTIs,
    respectively \\
$ssf^{i}_{ij},\ ssf^{j}_{ij}$
  & Safety stock of full RTIs held at the origin and destination
    node of route $(i,j)$, respectively \\
$sse^{i}_{ij},\ sse^{j}_{ij}$
  & Safety stock of empty RTIs held at the origin and destination
    node of route $(i,j)$, respectively \\
$\omega_{ij},\ \delta_{ij}$
  & Minimum and maximum shipment volume on route $(i,j)$ \\
$s^{\text{RTI}}$
  & Initial pool of RTIs available before optimisation \\
$p^{\text{RTI}}$
  & Unit purchase cost of one RTI \\
$M$
  & Sufficiently large constant (big-$M$) \\
\hline
\multicolumn{2}{|l|}{\textbf{Decision Variables}}\\ \hline
\multicolumn{2}{|l|}{\textit{Binary variables}}\\ \hline
$X_{ij}$, $ XF_{ij}$, $ XI_{ij}$, $ XE_{ij}$
  & Equal to 1 if route $(i,j)$ carries any RTIs, full RTIs,
    return inlays, or empty RTIs, respectively; 0 otherwise \\
\hline
\multicolumn{2}{|l|}{\textit{Daily flow variables}}\\ \hline
$N_{ij}$, $ NF_{ij}$, $ NI_{ij}$, $ NE_{ij}$
  & Daily average number of RTIs, full RTIs, return inlays, and
    empty RTIs on route $(i,j)$, respectively \\
\hline
\multicolumn{2}{|l|}{\textit{Per-shipment variables}}\\ \hline
$q_{ij}$
  & Queue time on route $(i,j)$: days between consecutive
    dispatches; \\
$NS_{ij}$, $ NSF_{ij}$, $ NSI_{ij}$, $ NSE_{ij}$
  & Total number of RTIs, full RTIs, return inlays, and empty RTIs
    per shipment on route $(i,j)$, respectively \\
$VS_{ij}$, $VSF_{ij}$, $VSI_{ij}$, $VSE_{ij}$
  & Total volume, full RTI volume, return inlay volume, and empty
    RTI volume per shipment on route $(i,j)$, respectively \\\hline
\multicolumn{2}{|l|}{\textit{RTI pool variables}}\\ \hline
$TNC_{ij}$, $ TNCF_{ij}$, $ TNCE_{ij}$, $ TNCI_{ij}$
  & Total RTIs, full RTIs, empty RTIs, and inlay RTIs allocated to route
    $(i,j)$, accounting for queue stock, in-transit stock, safety
    stock, and losses \\
$P$
  & Additional RTIs to purchase; $P \geq 0$ \\
\hline
\multicolumn{2}{|l|}{\textit{Cost variables}}\\ \hline
$TCS_{ij}$
  & Transport cost per shipment on route $(i,j)$ \\
$TC_{ij}$
  & Daily transport cost on route $(i,j)$ \\
\hline
\end{longtable}


% ══════════════════════════════════════════════════════════════════
%  OBJECTIVE FUNCTION
% ══════════════════════════════════════════════════════════════════

\paragraph{Objective function.}
Minimise total daily transport cost across all routes,
plus the amortised purchase cost of any additional RTIs required:
%
\begin{align}
  \min \quad
  \sum_{i,j \in V} TC_{ij}
  \;+\;
  p^{\text{RTI}} \cdot P
  \label{eq:objective}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  FLOW CONSERVATION
% ══════════════════════════════════════════════════════════════════

\paragraph{Flow conservation.}
The closed-loop balance must hold at every node:
%
\begin{align}
  \sum_{j\in V}\!\bigl(NF_{ij}+NI_{ij}+NE_{ij}\bigr)
  &=
  \sum_{j\in V}\!\bigl(NF_{ji}+NI_{ji}+NE_{ji}\bigr)
  && \forall\, i\in V
  \label{eq:conservation}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  ROUTE ACTIVATION
% ══════════════════════════════════════════════════════════════════

\paragraph{Route activation.}
A route is active if and only if it carries full, empty, or inlay RTIs:
%
\begin{align}
  3\cdot X_{ij} &\geq XF_{ij}+XE_{ij}+XI_{ij}
  && \forall\,(i,j)\in E \\
  X_{ij} &\leq XF_{ij}+XE_{ij}+XI_{ij}
  && \forall\,(i,j)\in E
\end{align}

% ══════════════════════════════════════════════════════════════════
%  RTI TYPE SELECTION
% ══════════════════════════════════════════════════════════════════

\paragraph{Full Routes activation}
A route carries full RTIs only if average daily demand is positive:
%
\begin{align}
  \mu_{ij} &\geq XF_{ij}
  && \forall\,(i,j)\in E
  \label{eq:type-selection}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  DEMAND SATISFACTION
% ══════════════════════════════════════════════════════════════════

\paragraph{Full RTIs route flow}
The daily full-RTI flow on route $(i,j)$ equals demand if and only
if the route is active:
%
\begin{align}
  NF_{ij} &= \mu_{ij} \cdot X_{ij}
  && \forall\,(i,j)\in E
  \label{eq:demand}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  INLAY RETURN FLOWS
% ══════════════════════════════════════════════════════════════════

\paragraph{Inlay return flows.}
Return inlays are sent back on the reverse route in proportion to
the full shipments that required them:
%
\begin{align}
  NI_{ji} &= ric_{ij} \cdot \mu_{ij} \cdot X_{ij}
  && \forall\,(i,j)\in E
  \label{eq:inlay}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  FLOW–BINARY CONSISTENCY
% ══════════════════════════════════════════════════════════════════

\paragraph{Flow--binary consistency.}
Each binary is active if and only if the corresponding daily flow
is positive:
%
\begin{align}
  NF_{ij} &\leq M \cdot XF_{ij}, \quad XF_{ij} \leq NF_{ij}
  && \forall\,(i,j)\in E \label{eq:binary-full}\\
  NI_{ij} &\leq M \cdot XI_{ij}, \quad XI_{ij} \leq NI_{ij}
  && \forall\,(i,j)\in E \label{eq:binary-inlay}\\
  NE_{ij} &\leq M \cdot XE_{ij}, \quad XE_{ij} \leq NE_{ij}
  && \forall\,(i,j)\in E \label{eq:binary-empty}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  PER-SHIPMENT QUANTITIES
% ══════════════════════════════════════════════════════════════════

\paragraph{Per-shipment RTI counts.}
RTIs accumulated between dispatches are proportional to the queue
time. These are \emph{nonlinear} and will be linearised in
Section~\ref{sec:linearisation}:
%
\begin{align}
  NSF_{ij} &= NF_{ij} \cdot q_{ij}
  && \forall\,(i,j)\in E \label{eq:ship-NF}\\
  NSI_{ij} &= NI_{ij} \cdot q_{ij}
  && \forall\,(i,j)\in E \label{eq:ship-NI}\\
  NSE_{ij} &= NE_{ij} \cdot q_{ij}
  && \forall\,(i,j)\in E \label{eq:ship-NE}\\
  NS_{ij}  &= NSF_{ij} + NSI_{ij} + NSE_{ij}
  && \forall\,(i,j)\in E \label{eq:ship-N}
\end{align}

\paragraph{Per-shipment volumes.}
Full and inlay RTIs occupy volume $v^{f}$; empty RTIs occupy $v^{e}$:
%
\begin{align}
  VSF_{ij} &= NF_{ij} \cdot v^{f} \cdot q_{ij}
  && \forall\,(i,j)\in E \label{eq:ship-VF}\\
  VSI_{ij} &= NI_{ij} \cdot v^{f} \cdot q_{ij}
  && \forall\,(i,j)\in E \label{eq:ship-VI}\\
  VSE_{ij} &= NE_{ij} \cdot v^{e} \cdot q_{ij}
  && \forall\,(i,j)\in E \label{eq:ship-VE}\\
  VS_{ij}  &= VSF_{ij} + VSI_{ij} + VSE_{ij}
  && \forall\,(i,j)\in E \label{eq:ship-vol}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  QUEUE TIME BOUNDS
% ══════════════════════════════════════════════════════════════════

\paragraph{Queue time bounds.}
The queue time is bounded and only meaningful when the route is active:
%
\begin{align}
  q^{\min} \cdot X_{ij}
  \;\leq\; q_{ij}
  \;\leq\; q^{\max} \cdot X_{ij}
  && \forall\,(i,j)\in E
  \label{eq:q-bounds}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  SHIPMENT VOLUME BOUNDS
% ══════════════════════════════════════════════════════════════════

\paragraph{Shipment volume bounds.}
Each active route must respect a minimum load and a maximum
vehicle capacity:
%
\begin{align}
  \omega_{ij} \cdot X_{ij}
  \;\leq\; VS_{ij}
  \;\leq\; \delta_{ij} \cdot X_{ij}
  && \forall\,(i,j)\in E
  \label{eq:vol-bounds}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  RTI POOL REQUIREMENTS
% ══════════════════════════════════════════════════════════════════

\paragraph{Total RTI pool requirements.}
The RTIs allocated to each route cover queue stock, in-transit
stock, safety stock at both endpoints, and a maintenance loss margin:
%
\begin{align}
  TNCF_{ij}
  &= (1+\alpha^{f})\!\left(
       NSF_{ij}
       + l_{ij}\cdot NF_{ij}
       + XF_{ij}\bigl(ssf^{i}_{ij}+ssf^{j}_{ij}\bigr)
     \right)
  && \forall\,(i,j)\in E
  \label{eq:pool-full}\\[4pt]
  TNCE_{ij}
  &= (1+\alpha^{e})\!\left(
       NSE_{ij}
       + l_{ij}\cdot NE_{ij}
       + XE_{ij}\bigl(sse^{i}_{ij}+sse^{j}_{ij}\bigr)
     \right)
  && \forall\,(i,j)\in E
  \label{eq:pool-empty}\\[4pt]
  TNCI_{ij}
  &= (1+\alpha^{f})\!\left(
       NSI_{ij}
       + l_{ij}\cdot NI_{ij}
     \right)
  && \forall\,(i,j)\in E
  \label{eq:pool-inlay}\\[4pt]
  TNC_{ij}
  &= TNCF_{ij} + TNCE_{ij} + TNCI_{ij}
  && \forall\,(i,j)\in E
  \label{eq:pool-total}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  RTI PURCHASE
% ══════════════════════════════════════════════════════════════════

\paragraph{RTI purchase.}
The network purchases any shortfall between the total pool
requirement and the existing stock:
%
\begin{align}
  \sum_{(i,j)\in E} TNC_{ij}
  &\leq s^{\text{RTI}} + P,
  \qquad P \geq 0
  \label{eq:purchase}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  DAILY TRANSPORT COSTS
% ══════════════════════════════════════════════════════════════════

\paragraph{Daily transport costs.}
The per-shipment cost combines a volumetric charge and a fixed
dispatch cost. Dividing by the queue time converts it to a daily
equivalent; this division is \emph{nonlinear} and will be
linearised in Section~\ref{sec:linearisation}:
%
\begin{align}
  TCS_{ij}
  &= VS_{ij} \cdot c_{ij}
     + X_{ij} \cdot f_{ij}
  && \forall\,(i,j)\in E
  \label{eq:cost-ship}\\[4pt]
  TC_{ij} \cdot q_{ij}
  &= TCS_{ij}
  && \forall\,(i,j)\in E
  \label{eq:cost-daily}
\end{align}

\subsection{Model variations}
The model presented above can be expanded to take into account different considerations. We introduce the following convention to reduce the notation overhaul. 
\input{notation/notation2.tex}

