\section{Compact}

% ══════════════════════════════════════════════════════════════════
%  NOMENCLATURE
% ══════════════════════════════════════════════════════════════════

\begin{longtable}{|p{0.22\textwidth}|p{0.77\textwidth}|}
\caption{Model nomenclature}
\label{tab:nomenclature}\\
\hline
\multicolumn{2}{|l|}{\textbf{Indices and Sets}}\\ \hline
$V$
  & Set of nodes representing manufacturing plants; $i, j \in V$ \\
$H \subseteq V$
  & Set of hub nodes; hubs may consolidate and redistribute empty
    RTIs of any type in transit \\
$E$
  & Set of directed edges representing potential transport lanes;
    $E \subseteq V \times V$ \\
$C$
  & Set of RTI types; $c \in C$ \\
$C_{ij} \subseteq C$
  & Set of RTI types admissible on lane $(i,j)$ \\
$\mathcal{M}$
  & Set of transport modes (e.g.\ FTL, groupage); $m \in \mathcal{M}$ \\
\hline
\multicolumn{2}{|l|}{\textbf{Parameters}}\\ \hline
$\mu_{cij}$
  & Daily demand on lane $(i,j)$ in type-$c$ RTI units;
    defined $\forall\,c \in C_{ij}$ \\
$ric_{cij}$
  & Fraction of type-$c$ full shipments on lane $(i,j)$ requiring
    a return inlay \\
$c_{ijm}$
  & Transport cost per unit volume on lane $(i,j)$ via mode $m$ \\
$f_{ijm}$
  & Fixed dispatch cost per shipment on lane $(i,j)$ via mode $m$ \\
$v^{f,c},\ v^{e,c}$
  & Volume of one full and one empty RTI of type $c$,
    respectively \\
$l_{ij}$
  & Transit time on lane $(i,j)$, in days \\
$\alpha^{f},\ \alpha^{e}$
  & Maintenance loss factor for full and empty RTIs, respectively \\
$ssf^{i,c}_{ij},\ ssf^{j,c}_{ij}$
  & Safety stock of full type-$c$ RTIs at the origin and
    destination of lane $(i,j)$ \\
$sse^{i,c}_{ij},\ sse^{j,c}_{ij}$
  & Safety stock of empty type-$c$ RTIs at the origin and
    destination of lane $(i,j)$ \\
$\omega_{ijm},\ \delta_{ijm}$
  & Minimum and maximum shipment volume on lane $(i,j)$
    via mode $m$ \\
$q^{\min}_{m},\ q^{\max}_{m}$
  & Minimum and maximum queue time permitted for mode $m$,
    in days \\
$s^{\text{RTI},c}$
  & Initial pool of type-$c$ RTIs before optimisation \\
$p^{\text{RTI},c}$
  & Unit purchase cost of one type-$c$ RTI \\
\hline
\multicolumn{2}{|l|}{\textbf{Decision Variables}}\\ \hline
\multicolumn{2}{|l|}{\textit{Binary variables (see
    Conventions~\ref{conv:notation} and~\ref{conv:reif})}}\\ \hline
$\hat{X}_{cij}$
  & Exactly-one selection binary: 1 if type $c$ is selected on
    lane $(i,j)$; exactly one type active per lane \\
$XF_{cijm}$
  & 1 if mode $m$ on lane $(i,j)$ carries full type-$c$ RTIs \\
$XI_{cijm}$
  & 1 if mode $m$ on lane $(i,j)$ carries type-$c$ inlays \\
$XE_{cijm}$
  & 1 if mode $m$ on lane $(i,j)$ carries empty type-$c$ RTIs \\
$\overline{XF}_{cij},\
 \overline{XI}_{cij},\
 \overline{XE}_{cij}$
  & \texttt{bool\_or} over $m$: 1 if any mode carries the
    corresponding flow of type $c$ on lane $(i,j)$ \\
$\overline{X}_{ijm}$
  & \texttt{bool\_or} over $c$ and flow types: 1 if mode $m$
    carries any RTI flow on lane $(i,j)$ \\
$EI_{ci}$
  & 1 if non-hub node $i \in V\setminus H$ receives empty
    type-$c$ RTIs from any lane \\
$EO_{ci}$
  & 1 if non-hub node $i \in V\setminus H$ dispatches empty
    type-$c$ RTIs on any lane \\
\hline
\multicolumn{2}{|l|}{\textit{Daily flow variables}}\\ \hline
$NF_{cijm}$
  & Daily average full type-$c$ RTIs on lane $(i,j)$ via mode $m$;
    non-negative integer \\
$NI_{cijm}$
  & Daily average type-$c$ inlays on lane $(i,j)$ via mode $m$;
    non-negative integer \\
$NE_{cijm}$
  & Daily average empty type-$c$ RTIs on lane $(i,j)$ via mode $m$;
    non-negative integer \\
\hline
\multicolumn{2}{|l|}{\textit{Per-shipment variables
    (\emph{bilinear}; see Section~\ref{sec:linearisation})}}\\ \hline
$q_{ijm}$
  & Queue time on lane $(i,j)$ via mode $m$, in days;
    non-negative integer \\
$NS_{cijm}$
  & Total type-$c$ RTIs per shipment on lane $(i,j)$ via mode $m$ \\
$VS_{ijm}$
  & Total volume per shipment on lane $(i,j)$ via mode $m$ \\
\hline
\multicolumn{2}{|l|}{\textit{RTI pool variables}}\\ \hline
$TNCF_{cij}$
  & Total full type-$c$ RTIs allocated to lane $(i,j)$ \\
$TNCE_{cij}$
  & Total empty type-$c$ RTIs allocated to lane $(i,j)$ \\
$TNCI_{cij}$
  & Total type-$c$ inlay RTIs allocated to lane $(i,j)$ \\
$P_{c}$
  & Additional type-$c$ RTIs to purchase; non-negative integer \\
\hline
\multicolumn{2}{|l|}{\textit{Cost variables}}\\ \hline
$TCS_{ijm}$
  & Transport cost per shipment on lane $(i,j)$ via mode $m$ \\
$TC_{ijm}$
  & Daily transport cost on lane $(i,j)$ via mode $m$ \\
\hline
\end{longtable}

% ══════════════════════════════════════════════════════════════════
%  CONVENTIONS
% ══════════════════════════════════════════════════════════════════

\begin{convention}[Index suppression and binary aggregation]
\label{conv:notation}
All variables are defined at the finest level $(i,j,c,m)$.
Suppressing indices follows three rules.

\medskip
\noindent\textbf{1. Continuous and integer variables} ---
suppression denotes summation:
\begin{align*}
  \phi_{cij}
    &\;\coloneqq\; \sum_{m\in\mathcal{M}} \phi_{cijm},
  &
  \phi_{ij}
    &\;\coloneqq\;
      \sum_{c\in C}\sum_{m\in\mathcal{M}} \phi_{cijm}
\end{align*}

\medskip
\noindent\textbf{2. Positional dot for same-set indices} ---
when both $i$ and $j$ belong to $V$, the suppressed position is
marked with a dot:
\begin{align*}
  \phi_{c}_{\cdot j m}
    &\;\coloneqq\; \sum_{i\in V} \phi_{cijm}
    &&\text{(sum over origin node)}, \\
  \phi_{c}_{i \cdot m}
    &\;\coloneqq\; \sum_{j\in V} \phi_{cijm}
    &&\text{(sum over destination node)}
\end{align*}

\medskip
\noindent\textbf{3. Binary aggregation via CP-SAT logical
primitives} --- suppressing an index on a binary produces an
aggregated binary defined by one of the following (see
Convention~\ref{conv:reif}):
\begin{itemize}
  \item \textit{Exactly-one} ($\hat{X}$, hat): exactly one
        element of the type set $C_{ij}$ is 1:
        \begin{align*}
          \hat{X}_{ij}
            \;\equiv\;
            \texttt{exactly\_one}\bigl(\hat{X}_{cij},\;
            c \in C_{ij}\bigr)
        \end{align*}
  \item \textit{OR aggregation} ($\overline{X}$, overline):
        at least one element of the set is 1,
        via \texttt{bool\_or}:
        \begin{align*}
          \overline{XF}_{cij} = 1
            &\;\Leftrightarrow\;
            \texttt{bool\_or}\bigl(XF_{cijm},\;
            m\in\mathcal{M}\bigr) \\
          \overline{XI}_{cij} = 1
            &\;\Leftrightarrow\;
            \texttt{bool\_or}\bigl(XI_{cijm},\;
            m\in\mathcal{M}\bigr) \\
          \overline{XE}_{cij} = 1
            &\;\Leftrightarrow\;
            \texttt{bool\_or}\bigl(XE_{cijm},\;
            m\in\mathcal{M}\bigr) \\
          \overline{X}_{ijm} = 1
            &\;\Leftrightarrow\;
            \texttt{bool\_or}\bigl(
              XF_{cijm},\,XI_{cijm},\,XE_{cijm},\;
              c\in C\bigr)
        \end{align*}
\end{itemize}
\end{convention}

\begin{convention}[CP-SAT reification and compact notation]
\label{conv:reif}
All logical relationships between binary variables and constraints
use the following three compact operators. No big-$M$ constants
appear anywhere in the model.

\medskip
\noindent\textbf{1. Gated equality} $\;b \;:\; \phi = k$\\
The binary $b$ gates a fixed-value assignment. This encodes the
pair of CP-SAT reifications:
\begin{align*}
  b = 1 &\;\Leftrightarrow\; \phi = k \\
  b = 0 &\;\Rightarrow\;    \phi = 0
\end{align*}
Reads as: ``$b$ enforces $\phi = k$; otherwise $\phi$ is zero.''
Implemented via \texttt{only\_enforce\_if} on both branches.

\medskip
\noindent\textbf{2. Activation reification} $\;b \;\doteq\; (\phi \geq 1)$\\
The binary $b$ is defined as the indicator of strict positivity.
Since all flow variables are non-negative integers, $\phi > 0$
is equivalent to $\phi \geq 1$ within CP-SAT integer arithmetic:
\begin{align*}
  b = 1 &\;\Leftrightarrow\; \phi \geq 1
\end{align*}
Reads as: ``$b$ is 1 if and only if $\phi$ is positive.''
Implemented via CP-SAT full reification.

\medskip
\noindent\textbf{3. Gated bounds} $\;b \;:\; \phi \in [l,\, u]$\\
The binary $b$ gates a range constraint. This encodes:
\begin{align*}
  b = 1 &\;\Rightarrow\; l \leq \phi \leq u \\
  b = 0 &\;\Rightarrow\; \phi = 0
\end{align*}
Reads as: ``$b$ enforces $\phi$ within $[l,u]$; otherwise $\phi$
is zero.'' Implemented via \texttt{only\_enforce\_if} on both
branches.

\medskip
\noindent\textbf{4. Logical set constraints.}
The following primitives operate directly on sets of Boolean
variables via dedicated CP-SAT propagators, achieving stronger
propagation than their linear-sum equivalents:
\begin{align*}
  \texttt{exactly\_one}(\mathcal{B})
    &\;\equiv\; \text{exactly one } b\in\mathcal{B}
      \text{ equals } 1 \\
  \texttt{at\_most\_one}(\mathcal{B})
    &\;\equiv\; \text{at most one } b\in\mathcal{B}
      \text{ equals } 1 \\
  \texttt{bool\_or}(\mathcal{B})
    &\;\equiv\; \text{at least one } b\in\mathcal{B}
      \text{ equals } 1
\end{align*}
\end{convention}

% ══════════════════════════════════════════════════════════════════
%  OBJECTIVE FUNCTION
% ══════════════════════════════════════════════════════════════════

\paragraph{Objective function.}
Minimise total daily transport cost plus the purchase cost of any
additional RTIs required:
%
\begin{align}
  \min \quad
  \sum_{(i,j)\in E}\sum_{m\in\mathcal{M}} TC_{ijm}
  \;+\;
  \sum_{c\in C} p^{\text{RTI},c} \cdot P_{c}
  \label{eq:objective}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  RTI TYPE SELECTION
% ══════════════════════════════════════════════════════════════════

\paragraph{RTI type selection.}
Each lane commits to exactly one RTI type from its admissible set:
%
\begin{align}
  \texttt{exactly\_one}\bigl(\hat{X}_{cij},\;
  c \in C_{ij}\bigr)
  && \forall\,(i,j) \in E
  \label{eq:type-selection}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  DEMAND SATISFACTION
% ══════════════════════════════════════════════════════════════════

\paragraph{Demand satisfaction.}
Using the gated equality operator, the full-RTI flow of type $c$
is fixed to its demand value when selected and zero otherwise:
%
\begin{align}
  \hat{X}_{cij} \;:\; NF_{cij} = \mu_{cij}
  && \forall\,(i,j)\in E,\ c\in C_{ij}
  \label{eq:demand}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  FLOW CONSERVATION
% ══════════════════════════════════════════════════════════════════

\paragraph{Flow conservation per RTI type.}
The closed-loop balance holds separately for each type at every
node. Aggregated lane flows are sums over $m$ per
Convention~\ref{conv:notation}:
%
\begin{align}
  \sum_{j\in V}\!\bigl(NF_{cij}+NI_{cij}+NE_{cij}\bigr)
  &=
  \sum_{j\in V}\!\bigl(NF_{c}_{ji}+NI_{c}_{ji}+NE_{c}_{ji}\bigr)
  && \forall\, i\in V,\ c\in C
  \label{eq:conservation}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  INLAY RETURN FLOWS
% ══════════════════════════════════════════════════════════════════

\paragraph{Inlay return flows.}
The return inlay flow on the reverse lane is gated by the type
selection on the forward lane:
%
\begin{align}
  \hat{X}_{cij} \;:\; NI_{c}_{ji}
    = ric_{cij}\cdot\mu_{cij}
  && \forall\,(i,j)\in E,\ c\in C_{ij}
  \label{eq:inlay}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  FLOW--BINARY CONSISTENCY
% ══════════════════════════════════════════════════════════════════

\paragraph{Flow--binary consistency.}
Each type-mode binary is defined as the activation indicator of
its corresponding flow. The aggregated overline forms follow from
the \texttt{bool\_or} definitions in Convention~\ref{conv:notation}:
%
\begin{align}
  XF_{cijm} &\;\doteq\; (NF_{cijm} \geq 1)
  && \forall\,(i,j)\in E,\ c\in C,\ m\in\mathcal{M}
  \label{eq:binary-full}\\
  XI_{cijm} &\;\doteq\; (NI_{cijm} \geq 1)
  && \forall\,(i,j)\in E,\ c\in C,\ m\in\mathcal{M}
  \label{eq:binary-inlay}\\
  XE_{cijm} &\;\doteq\; (NE_{cijm} \geq 1)
  && \forall\,(i,j)\in E,\ c\in C,\ m\in\mathcal{M}
  \label{eq:binary-empty}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  HUB STRUCTURE
% ══════════════════════════════════════════════════════════════════

\paragraph{Hub and non-hub node structure.}
Hub nodes $i\in H$ are unrestricted. At non-hub nodes
$i\in V\setminus H$, the incoming and outgoing empty-flow
indicators are defined via activation reification (dot notation
of Convention~\ref{conv:notation}), then constrained to be
mutually exclusive:
%
\begin{align}
  EI_{ci}
    &\;\doteq\; (NE_{c}_{\cdot i} \geq 1)
  && \forall\, i\in V\setminus H,\ c\in C
  \label{eq:hub-EI}\\
  EO_{ci}
    &\;\doteq\; (NE_{c}_{i\cdot} \geq 1)
  && \forall\, i\in V\setminus H,\ c\in C
  \label{eq:hub-EO}\\
  \texttt{at\_most\_one}&\bigl(EI_{ci},\, EO_{ci}\bigr)
  && \forall\, i\in V\setminus H,\ c\in C
  \label{eq:non-hub}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  PER-SHIPMENT QUANTITIES
% ══════════════════════════════════════════════════════════════════

\paragraph{Per-shipment quantities.}
RTIs and volume accumulated between dispatches are proportional to
the queue time. These products are \emph{bilinear} and will be
linearised in Section~\ref{sec:linearisation}:
%
\begin{align}
  NS_{cijm}
  &= \bigl(NF_{cijm}+NI_{cijm}+NE_{cijm}\bigr)
     \cdot q_{ijm}
  && \forall\,(i,j)\in E,\ c\in C,\ m\in\mathcal{M}
  \label{eq:ship-N}\\
  VS_{ijm}
  &= \sum_{c\in C}\!\Bigl(
       NF_{cijm}\cdot v^{f,c}
      +NI_{cijm}\cdot v^{f,c}
      +NE_{cijm}\cdot v^{e,c}
     \Bigr)\cdot q_{ijm}
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:ship-vol}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  SHIPMENT VOLUME AND QUEUE TIME BOUNDS
% ══════════════════════════════════════════════════════════════════

\paragraph{Shipment volume and queue time bounds.}
The mode activation binary gates both the shipment volume and the
queue time within their permitted ranges; inactive modes force
both to zero:
%
\begin{align}
  \overline{X}_{ijm}
    &\;:\; VS_{ijm} \in [\omega_{ijm},\, \delta_{ijm}]
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:vol-bounds}\\[4pt]
  \overline{X}_{ijm}
    &\;:\; q_{ijm} \in [q^{\min}_{m},\, q^{\max}_{m}]
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:q-bounds}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  RTI POOL REQUIREMENTS
% ══════════════════════════════════════════════════════════════════

\paragraph{Total RTI pool requirements.}
RTIs allocated to each lane cover queue stock, in-transit stock,
safety stock at both endpoints (triggered by the \texttt{bool\_or}
binaries $\overline{XF}_{cij}$ and $\overline{XE}_{cij}$
of Convention~\ref{conv:notation}), and a maintenance loss margin:
%
\begin{align}
  TNCF_{cij}
  &= (1+\alpha^{f})\!\left(
       NS_{cij}
       + l_{ij}\cdot NF_{cij}
       + \overline{XF}_{cij}
         \bigl(ssf^{i,c}_{ij}+ssf^{j,c}_{ij}\bigr)
     \right)
  && \forall\,(i,j)\in E,\ c\in C
  \label{eq:pool-full}\\[4pt]
  TNCE_{cij}
  &= (1+\alpha^{e})\!\left(
       NS_{cij}
       + l_{ij}\cdot NE_{cij}
       + \overline{XE}_{cij}
         \bigl(sse^{i,c}_{ij}+sse^{j,c}_{ij}\bigr)
     \right)
  && \forall\,(i,j)\in E,\ c\in C
  \label{eq:pool-empty}\\[4pt]
  TNCI_{cij}
  &= (1+\alpha^{f})\!\left(
       NS_{cij}
       + l_{ij}\cdot NI_{cij}
     \right)
  && \forall\,(i,j)\in E,\ c\in C
  \label{eq:pool-inlay}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  RTI PURCHASE
% ══════════════════════════════════════════════════════════════════

\paragraph{RTI purchase.}
The network purchases any shortfall between the total pool
requirement and the existing stock; a surplus remains idle:
%
\begin{align}
  \sum_{(i,j)\in E}\!\bigl(
    TNCF_{cij}+TNCE_{cij}+TNCI_{cij}
  \bigr)
  &\leq s^{\text{RTI},c} + P_{c}
  && \forall\, c\in C,\quad P_{c}\geq 0
  \label{eq:purchase}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  DAILY TRANSPORT COSTS
% ══════════════════════════════════════════════════════════════════

\paragraph{Daily transport costs.}
The per-shipment cost combines a volumetric and a fixed dispatch
charge. The mode activation binary gates the bilinear daily cost
relation; inactive modes are forced to zero cost:
%
\begin{align}
  TCS_{ijm}
  &= VS_{ijm}\cdot c_{ijm}
     + \overline{X}_{ijm}\cdot f_{ijm}
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:cost-ship}\\[4pt]
  \overline{X}_{ijm}
    &\;:\; TC_{ijm}\cdot q_{ijm} = TCS_{ijm}
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:cost-daily}
\end{align}

hello
\begin{equation}
\bigvee_{c \in C_{ij}}
\begin{bmatrix}
  \hat{X}_{cij} \\
  NF_{cij} = \mu_{cij} \\
  NI_{c}_{ji} = ric_{cij}\cdot\mu_{cij} \\
  \text{(all type-}c\text{ quantities active)}
\end{bmatrix}
\end{equation}
