\section{Mathematical Model}

% ══════════════════════════════════════════════════════════════════
%  NOMENCLATURE
% ══════════════════════════════════════════════════════════════════

\begin{longtable}{|p{0.22\textwidth}|p{0.77\textwidth}|}
\caption{Model nomenclature}
\label{tab:nomenclature}\\
\hline
\multicolumn{2}{|l|}{\textbf{Indices and Sets}}\\ \hline
$V$
  & Set of nodes representing manufacturing plants; $i, j \in V$ \\
$H \subseteq V$
  & Set of hub nodes; hubs may consolidate and redistribute empty
    RTIs of any type in transit \\
$E$
  & Set of directed edges representing potential transport lanes;
    $E \subseteq V \times V$ \\
$C$
  & Set of RTI types; $c \in C$ \\
$C_{ij} \subseteq C$
  & Set of RTI types admissible on lane $(i,j)$ \\
$\mathcal{M}$
  & Set of transport modes (e.g.\ FTL, groupage); $m \in \mathcal{M}$ \\
\hline
\multicolumn{2}{|l|}{\textbf{Parameters}}\\ \hline
$\mu_{cij}$
  & Daily demand on lane $(i,j)$ in type-$c$ RTI units;
    defined $\forall\,c \in C_{ij}$ \\
$ric_{cij}$
  & Fraction of type-$c$ full shipments on lane $(i,j)$ requiring
    a return inlay \\
$c_{ijm}$
  & Transport cost per unit volume on lane $(i,j)$ via mode $m$ \\
$f_{ijm}$
  & Fixed dispatch cost per shipment on lane $(i,j)$ via mode $m$ \\
$v^{f,c},\ v^{e,c}$
  & Volume of one full and one empty RTI of type $c$,
    respectively \\
$l_{ij}$
  & Transit time on lane $(i,j)$, in days \\
$\alpha^{f},\ \alpha^{e}$
  & Maintenance loss factor for full and empty RTIs, respectively \\
$ssf^{i,c}_{ij},\ ssf^{j,c}_{ij}$
  & Safety stock of full type-$c$ RTIs at the origin and
    destination of lane $(i,j)$ \\
$sse^{i,c}_{ij},\ sse^{j,c}_{ij}$
  & Safety stock of empty type-$c$ RTIs at the origin and
    destination of lane $(i,j)$ \\
$\omega_{ijm},\ \delta_{ijm}$
  & Minimum and maximum shipment volume on lane $(i,j)$
    via mode $m$ \\
$q^{\min}_{m},\ q^{\max}_{m}$
  & Minimum and maximum queue time permitted for mode $m$,
    in days \\
$s^{\text{RTI},c}$
  & Initial pool of type-$c$ RTIs before optimisation \\
$p^{\text{RTI},c}$
  & Unit purchase cost of one type-$c$ RTI \\
\hline
\multicolumn{2}{|l|}{\textbf{Decision Variables}}\\ \hline
\multicolumn{2}{|l|}{\textit{Binary variables (see
    Conventions~\ref{conv:notation} and~\ref{conv:reif})}}\\ \hline
$\hat{X}_{cij}$
  & Exactly-one selection binary: 1 if type $c$ is selected on
    lane $(i,j)$; exactly one type active per lane \\
$XF_{cijm}$
  & 1 if mode $m$ on lane $(i,j)$ carries full type-$c$ RTIs \\
$XI_{cijm}$
  & 1 if mode $m$ on lane $(i,j)$ carries type-$c$ inlays \\
$XE_{cijm}$
  & 1 if mode $m$ on lane $(i,j)$ carries empty type-$c$ RTIs \\
$\overline{XF}_{cij},\
 \overline{XI}_{cij},\
 \overline{XE}_{cij}$
  & \texttt{bool\_or} over $m$: 1 if any mode carries the
    corresponding flow of type $c$ on lane $(i,j)$ \\
$\overline{X}_{ijm}$
  & \texttt{bool\_or} over $c$ and flow types: 1 if mode $m$
    carries any RTI flow on lane $(i,j)$ \\
$EI_{ci}$
  & 1 if non-hub node $i \in V\setminus H$ receives empty
    type-$c$ RTIs from any lane \\
$EO_{ci}$
  & 1 if non-hub node $i \in V\setminus H$ dispatches empty
    type-$c$ RTIs on any lane \\
\hline
\multicolumn{2}{|l|}{\textit{Daily flow variables}}\\ \hline
$NF_{cijm}$
  & Daily average full type-$c$ RTIs on lane $(i,j)$ via mode $m$;
    non-negative integer \\
$NI_{cijm}$
  & Daily average type-$c$ inlays on lane $(i,j)$ via mode $m$;
    non-negative integer \\
$NE_{cijm}$
  & Daily average empty type-$c$ RTIs on lane $(i,j)$ via mode $m$;
    non-negative integer \\
\hline
\multicolumn{2}{|l|}{\textit{Per-shipment variables
    (\emph{bilinear}; see Section~\ref{sec:linearisation})}}\\ \hline
$q_{ijm}$
  & Queue time on lane $(i,j)$ via mode $m$, in days;
    non-negative integer \\
$NS_{cijm}$
  & Total type-$c$ RTIs per shipment on lane $(i,j)$ via mode $m$;
    non-negative integer \\
$VS_{ijm}$
  & Total volume per shipment on lane $(i,j)$ via mode $m$ \\
\hline
\multicolumn{2}{|l|}{\textit{RTI pool variables}}\\ \hline
$TNCF_{cij}$
  & Total full type-$c$ RTIs allocated to lane $(i,j)$ \\
$TNCE_{cij}$
  & Total empty type-$c$ RTIs allocated to lane $(i,j)$ \\
$TNCI_{cij}$
  & Total type-$c$ inlay RTIs allocated to lane $(i,j)$ \\
$P_{c}$
  & Additional type-$c$ RTIs to purchase; non-negative integer \\
\hline
\multicolumn{2}{|l|}{\textit{Cost variables}}\\ \hline
$TCS_{ijm}$
  & Transport cost per shipment on lane $(i,j)$ via mode $m$ \\
$TC_{ijm}$
  & Daily transport cost on lane $(i,j)$ via mode $m$ \\
\hline
\end{longtable}

% ══════════════════════════════════════════════════════════════════
%  CONVENTIONS
% ══════════════════════════════════════════════════════════════════

\begin{convention}[Index suppression and binary aggregation]
\label{conv:notation}
All variables are defined at the finest level $(i,j,c,m)$.
Suppressing indices follows three rules.

\medskip
\noindent\textbf{1. Continuous and integer variables} ---
suppression denotes summation:
\begin{align*}
  \phi_{cij}
    &\;\coloneqq\; \sum_{m\in\mathcal{M}} \phi_{cijm},
  &
  \phi_{ij}
    &\;\coloneqq\;
      \sum_{c\in C}\sum_{m\in\mathcal{M}} \phi_{cijm}
\end{align*}

\medskip
\noindent\textbf{2. Positional dot for same-set indices} ---
when both $i$ and $j$ belong to $V$, the suppressed position is
marked with a dot to avoid ambiguity:
\begin{align*}
  \phi_{c}_{\cdot j m}
    &\;\coloneqq\; \sum_{i\in V} \phi_{cijm}
    &&\text{(sum over origin node)}, \\
  \phi_{c}_{i \cdot m}
    &\;\coloneqq\; \sum_{j\in V} \phi_{cijm}
    &&\text{(sum over destination node)}
\end{align*}
The dot is not required for $c \in C$ or $m \in \mathcal{M}$
since no other active index shares those sets.

\medskip
\noindent\textbf{3. Binary aggregation via CP-SAT logical
primitives} --- suppressing an index on a binary variable
produces an aggregated binary whose semantics is defined by one
of the following logical set constraints (see
Convention~\ref{conv:reif}):

\begin{itemize}
  \item \textit{Exactly-one} ($\hat{X}$, hat): applied to the
        type index $c$; exactly one element of the set is 1:
        \begin{align*}
          \hat{X}_{ij} = 1
            \;\equiv\;
            \texttt{exactly\_one}\bigl(\hat{X}_{cij},\;
            c \in C_{ij}\bigr)
        \end{align*}

  \item \textit{OR aggregation} ($\overline{X}$, overline):
        active if at least one element of the set is 1,
        expressed via \texttt{bool\_or}. Two levels are used
        in this model:
        \begin{align*}
          \overline{XF}_{cij} = 1
            &\;\Leftrightarrow\;
            \texttt{bool\_or}\bigl(XF_{cijm},\;
            m\in\mathcal{M}\bigr) \\
          \overline{XI}_{cij} = 1
            &\;\Leftrightarrow\;
            \texttt{bool\_or}\bigl(XI_{cijm},\;
            m\in\mathcal{M}\bigr) \\
          \overline{XE}_{cij} = 1
            &\;\Leftrightarrow\;
            \texttt{bool\_or}\bigl(XE_{cijm},\;
            m\in\mathcal{M}\bigr) \\
          \overline{X}_{ijm} = 1
            &\;\Leftrightarrow\;
            \texttt{bool\_or}\bigl(
              XF_{cijm},\,XI_{cijm},\,XE_{cijm},\;
              c\in C\bigr)
        \end{align*}
\end{itemize}
\end{convention}

\begin{convention}[CP-SAT reification and logical primitives]
\label{conv:reif}
All logical relationships between binary variables and constraints
are expressed using the native CP-SAT primitives described below.
No big-$M$ constants are used anywhere in the model.

\medskip
\noindent\textbf{1. Half-reification} (\texttt{only\_enforce\_if},
implication $\Rightarrow$):
\begin{align*}
  b = 1 \;\Rightarrow\; \bigl[\,g(x) \leq 0\,\bigr]
\end{align*}
The constraint $g(x)\leq 0$ is enforced only when $b=1$; when
$b=0$ the constraint is relaxed entirely. Corresponds directly
to \texttt{model.add(\ldots).only\_enforce\_if(b)} in CP-SAT.

\medskip
\noindent\textbf{2. Full reification} (if and only if,
$\Leftrightarrow$):
\begin{align*}
  b = 1 \;\Leftrightarrow\; \bigl[\,g(x) \leq 0\,\bigr]
\end{align*}
The binary $b$ is 1 if and only if the constraint is satisfied.
Implemented as the pair:
$b=1\Rightarrow g(x)\leq 0$ and $b=0\Rightarrow g(x)>0$,
using CP-SAT's native reification support.

\medskip
\noindent\textbf{3. Logical set constraints} (propagate without
linear arithmetic):
\begin{align*}
  \texttt{exactly\_one}(\mathcal{B})
    &\;\equiv\;
    \text{exactly one } b\in\mathcal{B} \text{ equals } 1 \\
  \texttt{at\_most\_one}(\mathcal{B})
    &\;\equiv\;
    \text{at most one } b\in\mathcal{B} \text{ equals } 1 \\
  \texttt{bool\_or}(\mathcal{B})
    &\;\equiv\;
    \text{at least one } b\in\mathcal{B} \text{ equals } 1
\end{align*}
These are enforced by dedicated CP-SAT propagators
(\texttt{add\_exactly\_one}, \texttt{add\_at\_most\_one},
\texttt{add\_bool\_or}) and achieve stronger propagation
than their linear-sum equivalents.

\medskip
\noindent\textbf{4. Integer strict positivity.}
Since all flow variables are non-negative integers, the
condition $\phi > 0$ is always written as $\phi \geq 1$,
remaining within the linear integer arithmetic of CP-SAT.
\end{convention}

% ══════════════════════════════════════════════════════════════════
%  OBJECTIVE FUNCTION
% ══════════════════════════════════════════════════════════════════

\paragraph{Objective function.}
Minimise total daily transport cost plus the purchase cost of any
additional RTIs required:
%
\begin{align}
  \min \quad
  \sum_{(i,j)\in E}\sum_{m\in\mathcal{M}} TC_{ijm}
  \;+\;
  \sum_{c\in C} p^{\text{RTI},c} \cdot P_{c}
  \label{eq:objective}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  RTI TYPE SELECTION
% ══════════════════════════════════════════════════════════════════

\paragraph{RTI type selection.}
Each lane commits to exactly one RTI type from its admissible set.
This is enforced by a dedicated CP-SAT propagator:
%
\begin{align}
  \texttt{exactly\_one}\bigl(\hat{X}_{cij},\; c \in C_{ij}\bigr)
  && \forall\,(i,j) \in E
  \label{eq:type-selection}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  DEMAND SATISFACTION
% ══════════════════════════════════════════════════════════════════

\paragraph{Demand satisfaction.}
The total full-RTI flow of type $c$ equals the type-specific
demand if and only if that type is selected; it is zero otherwise:
%
\begin{align}
  \hat{X}_{cij} = 1
    &\;\Leftrightarrow\;
    \Bigl[\,NF_{cij} = \mu_{cij}\,\Bigr]
  && \forall\,(i,j)\in E,\ c\in C_{ij}
  \label{eq:demand-on}\\
  \hat{X}_{cij} = 0
    &\;\Rightarrow\;
    \Bigl[\,NF_{cij} = 0\,\Bigr]
  && \forall\,(i,j)\in E,\ c\in C_{ij}
  \label{eq:demand-off}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  FLOW CONSERVATION
% ══════════════════════════════════════════════════════════════════

\paragraph{Flow conservation per RTI type.}
The closed-loop balance holds separately for each type at every
node, whether hub or not. Using Convention~\ref{conv:notation},
the aggregated lane flows are sums over $m$:
%
\begin{align}
  \sum_{j\in V}\!\bigl(NF_{cij}+NI_{cij}+NE_{cij}\bigr)
  &=
  \sum_{j\in V}\!\bigl(NF_{c}_{ji}+NI_{c}_{ji}+NE_{c}_{ji}\bigr)
  && \forall\, i\in V,\ c\in C
  \label{eq:conservation}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  INLAY RETURN FLOWS
% ══════════════════════════════════════════════════════════════════

\paragraph{Inlay return flows.}
Return inlays of type $c$ on the reverse lane are set if and only
if type $c$ is selected on the forward lane:
%
\begin{align}
  \hat{X}_{cij} = 1
    &\;\Leftrightarrow\;
    \Bigl[\,NI_{c}_{ji} = ric_{cij}\cdot\mu_{cij}\,\Bigr]
  && \forall\,(i,j)\in E,\ c\in C_{ij}
  \label{eq:inlay-on}\\
  \hat{X}_{cij} = 0
    &\;\Rightarrow\;
    \Bigl[\,NI_{c}_{ji} = 0\,\Bigr]
  && \forall\,(i,j)\in E,\ c\in C_{ij}
  \label{eq:inlay-off}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  FLOW--BINARY CONSISTENCY
% ══════════════════════════════════════════════════════════════════

\paragraph{Flow--binary consistency.}
Each type-mode binary is fully reified against its corresponding
integer flow. Since all flows are non-negative integers,
$\geq 1$ is equivalent to strict positivity
(Convention~\ref{conv:reif}, rule~4). The aggregated overline
forms $\overline{XF}_{cij}$, $\overline{XI}_{cij}$,
$\overline{XE}_{cij}$, and $\overline{X}_{ijm}$ follow from
the \texttt{bool\_or} definitions in Convention~\ref{conv:notation}:
%
\begin{align}
  XF_{cijm} = 1
    &\;\Leftrightarrow\;
    \Bigl[\,NF_{cijm} \geq 1\,\Bigr]
  && \forall\,(i,j)\in E,\ c\in C,\ m\in\mathcal{M}
  \label{eq:binary-full}\\
  XI_{cijm} = 1
    &\;\Leftrightarrow\;
    \Bigl[\,NI_{cijm} \geq 1\,\Bigr]
  && \forall\,(i,j)\in E,\ c\in C,\ m\in\mathcal{M}
  \label{eq:binary-inlay}\\
  XE_{cijm} = 1
    &\;\Leftrightarrow\;
    \Bigl[\,NE_{cijm} \geq 1\,\Bigr]
  && \forall\,(i,j)\in E,\ c\in C,\ m\in\mathcal{M}
  \label{eq:binary-empty}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  HUB STRUCTURE
% ══════════════════════════════════════════════════════════════════

\paragraph{Hub and non-hub node structure.}
Hub nodes $i\in H$ are unrestricted with respect to empty RTI
flows. At non-hub nodes $i\in V\setminus H$, the binaries
$EI_{ci}$ and $EO_{ci}$ are fully reified against the
aggregated incoming and outgoing empty flows (using the dot
notation of Convention~\ref{conv:notation}), and are then
constrained to be mutually exclusive via
\texttt{at\_most\_one}:
%
\begin{align}
  EI_{ci} = 1
    &\;\Leftrightarrow\;
    \Bigl[\,NE_{c}_{\cdot i} \geq 1\,\Bigr]
  && \forall\, i\in V\setminus H,\ c\in C
  \label{eq:hub-EI}\\
  EO_{ci} = 1
    &\;\Leftrightarrow\;
    \Bigl[\,NE_{c}_{i\cdot} \geq 1\,\Bigr]
  && \forall\, i\in V\setminus H,\ c\in C
  \label{eq:hub-EO}\\
  \texttt{at\_most\_one}\bigl(EI_{ci},\, EO_{ci}\bigr)
  && \forall\, i\in V\setminus H,\ c\in C
  \label{eq:non-hub}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  PER-SHIPMENT QUANTITIES
% ══════════════════════════════════════════════════════════════════

\paragraph{Per-shipment quantities.}
RTIs and volume accumulated between dispatches are proportional to
the queue time. These products are \emph{bilinear} and will be
linearised in Section~\ref{sec:linearisation}:
%
\begin{align}
  NS_{cijm}
  &= \bigl(NF_{cijm}+NI_{cijm}+NE_{cijm}\bigr)
     \cdot q_{ijm}
  && \forall\,(i,j)\in E,\ c\in C,\ m\in\mathcal{M}
  \label{eq:ship-N}\\
  VS_{ijm}
  &= \sum_{c\in C}\!\Bigl(
       NF_{cijm}\cdot v^{f,c}
      +NI_{cijm}\cdot v^{f,c}
      +NE_{cijm}\cdot v^{e,c}
     \Bigr)\cdot q_{ijm}
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:ship-vol}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  SHIPMENT VOLUME AND QUEUE TIME BOUNDS
% ══════════════════════════════════════════════════════════════════

\paragraph{Shipment volume and queue time bounds.}
When mode $m$ is active on lane $(i,j)$, shipment volume and
queue time must lie within their permitted ranges; when inactive,
both are forced to zero:
%
\begin{align}
  \overline{X}_{ijm} = 1
    &\;\Rightarrow\;
    \Bigl[\,\omega_{ijm} \leq VS_{ijm} \leq \delta_{ijm}\,\Bigr]
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:vol-bounds-on}\\
  \overline{X}_{ijm} = 0
    &\;\Rightarrow\;
    \Bigl[\,VS_{ijm} = 0\,\Bigr]
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:vol-bounds-off}\\[4pt]
  \overline{X}_{ijm} = 1
    &\;\Rightarrow\;
    \Bigl[\,q^{\min}_{m} \leq q_{ijm} \leq q^{\max}_{m}\,\Bigr]
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:q-bounds-on}\\
  \overline{X}_{ijm} = 0
    &\;\Rightarrow\;
    \Bigl[\,q_{ijm} = 0\,\Bigr]
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:q-bounds-off}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  RTI POOL REQUIREMENTS
% ══════════════════════════════════════════════════════════════════

\paragraph{Total RTI pool requirements.}
RTIs allocated to each lane must cover queue stock, in-transit
stock, safety stock at both endpoints (triggered only when the
flow type is active, via the \texttt{bool\_or} binaries
$\overline{XF}_{cij}$ and $\overline{XE}_{cij}$ of
Convention~\ref{conv:notation}), and a maintenance loss margin:
%
\begin{align}
  TNCF_{cij}
  &= (1+\alpha^{f})\!\left(
       NS_{cij}
       + l_{ij}\cdot NF_{cij}
       + \overline{XF}_{cij}
         \bigl(ssf^{i,c}_{ij}+ssf^{j,c}_{ij}\bigr)
     \right)
  && \forall\,(i,j)\in E,\ c\in C
  \label{eq:pool-full}\\[4pt]
  TNCE_{cij}
  &= (1+\alpha^{e})\!\left(
       NS_{cij}
       + l_{ij}\cdot NE_{cij}
       + \overline{XE}_{cij}
         \bigl(sse^{i,c}_{ij}+sse^{j,c}_{ij}\bigr)
     \right)
  && \forall\,(i,j)\in E,\ c\in C
  \label{eq:pool-empty}\\[4pt]
  TNCI_{cij}
  &= (1+\alpha^{f})\!\left(
       NS_{cij}
       + l_{ij}\cdot NI_{cij}
     \right)
  && \forall\,(i,j)\in E,\ c\in C
  \label{eq:pool-inlay}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  RTI PURCHASE
% ══════════════════════════════════════════════════════════════════

\paragraph{RTI purchase.}
The network purchases any shortfall between the total pool
requirement and the existing stock; a surplus remains idle:
%
\begin{align}
  \sum_{(i,j)\in E}\!\bigl(
    TNCF_{cij}+TNCE_{cij}+TNCI_{cij}
  \bigr)
  &\leq s^{\text{RTI},c} + P_{c}
  && \forall\, c\in C,\quad P_{c}\geq 0
  \label{eq:purchase}
\end{align}

% ══════════════════════════════════════════════════════════════════
%  DAILY TRANSPORT COSTS
% ══════════════════════════════════════════════════════════════════

\paragraph{Daily transport costs.}
The per-shipment cost combines a volumetric and a fixed dispatch
charge. Dividing by the queue time gives the daily equivalent;
this product is \emph{bilinear} and will be linearised in
Section~\ref{sec:linearisation}. The cost constraint is
enforced only when the mode is active; inactive modes are
forced to zero cost:
%
\begin{align}
  TCS_{ijm}
  &= VS_{ijm}\cdot c_{ijm}
     + \overline{X}_{ijm}\cdot f_{ijm}
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:cost-ship}\\[4pt]
  \overline{X}_{ijm} = 1
    &\;\Rightarrow\;
    \Bigl[\,TC_{ijm}\cdot q_{ijm} = TCS_{ijm}\,\Bigr]
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:cost-daily-on}\\
  \overline{X}_{ijm} = 0
    &\;\Rightarrow\;
    \Bigl[\,TC_{ijm} = 0\,\Bigr]
  && \forall\,(i,j)\in E,\ m\in\mathcal{M}
  \label{eq:cost-daily-off}
\end{align}
